Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-24 paper/paper.tex
new figure

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{A representative result from the tree classification algorithm. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the number of samples and the value of the
number of samples in each of the classification classes.  We use two
classes: low $\chi^2/d.o.f. < 35$ and $\chi^2/d.o.f>35$. 
In this example the best way to increase the probability to find a
model with  low $\chi^2/d.o.f.$ is having $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
\label{fig:tree}}
\end{center}
\end{figure*}
